---
title: "FRaME"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FRaME}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(frame)
library(dplyr)
library(extraDistr)
library(kableExtra)
library(rmarkdown)
```


This script runs a deterministic prediction using a legacy file, which is the old .txt setup
The steps are to import the file, run it, then load the database.

## 1. LOAD THE INPUT FILES AND CONSTRUCT A PARAMETER TABLE
Enter the full path to each file in quotes

```{r params_input}
record <- 1
data(f_site)
data(f_structure)
data(f_flora)
data(f_traits)
input <- paramBuilder(f_site, f_structure, f_flora, f_traits, record)


```


## 2. RUN THE MODEL
Specify the name of the input file, name the sqLite database that it will write to, and whether you want each model run to overwrite the last (db.recreate = TRUE), or append to it. The model will first check that Java is up to date, then print "TRUE" if it could run the input file



```{r ffm_run, eval = FALSE, results= 'hide'}
ffm_run(input, db.path = "out.db", db.recreate = TRUE)
```





## 3. LOAD THE DATABASE

```{r db_load}
results<-ffm_db_load("out.db")
```



The database is a list of 7 dataframes, shown and described here: 
Gives summary flame dimensions (m, radians) for each stratum. 'repid' will always be 1 for single runs. A runIndex of 2 indicates an active crown fire, causing the model to re-run with the shelter of the canopy removed
```{r flamesummaries}
results$FlameSummaries %>%
 kbl() %>% 
  kable_material(c("striped", "hover"))
```
  
Gives x & y coordinates for the base (x0, y0) and top (x1, y1) of ignited segments in the named species, per second. The length of the segment 'length', and 'flameLength' is the length of the segment plus the flame extending beyond pathType is 'plant' if it occurs in a sinple plant, or 'stratum' if the fire is spread from plant to plant


```{r ignitionpaths}
results$IgnitionPaths %>% 
  paged_table()
```



Gives ROS (m/s) in each stratum
```{r ros}
results$ROS %>% 
  kbl() %>% 
  kable_material(c("striped", "hover"))
```

Lists the types of runIndex described above


```{r runs}
results$Runs %>% 
  kbl() %>% 
  kable_material(c("striped", "hover"))
```



Gives the input site conditions in m/s, degrees C, radians, kg/sqm, m, and proportion

```{r sites}
results$Sites%>% 
  kbl() %>% 
  kable_material(c("striped", "hover"))
```


Lists the component plant strata

```{r strata}
results$Strata%>% 
  kbl() %>% 
  kable_material(c("striped", "hover"))
```

Gives wind speed at ground level (m/s), and summary flame dimensions (m, radians) for fire in surface litter

```{r surfaceresults}

results$SurfaceResults %>% 
  kbl() %>% 
  kable_material(c("striped", "hover"))

```








